### 2024-07-19 getting-started.qmd
20240719 - fix errors and cleanup
20240719 - clean up
20240719 - remove `here` package dependency

library("here")

# Downloaded Data
load(file = here("data", "nfl_players.RData"))
load(file = here("data", "nfl_teams.RData"))
load(file = here("data", "nfl_rosters.RData"))
load(file = here("data", "nfl_rosters_weekly.RData"))
load(file = here("data", "nfl_schedules.RData"))
load(file = here("data", "nfl_combine.RData"))
load(file = here("data", "nfl_draftPicks.RData"))
load(file = here("data", "nfl_depthCharts.RData"))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation.RData", fsep = ""))
load(file = here("data", "nfl_actualStats_weekly.RData"))
load(file = here("data", "nfl_injuries.RData"))
load(file = here("data", "nfl_snapCounts.RData"))
load(file = here("data", "nfl_espnQBR.RData"))
load(file = here("data", "nfl_nextGenStats_weekly.RData"))
load(file = here("data", "nfl_advancedStatsPFR.RData"))
load(file = here("data", "nfl_playerContracts.RData"))
load(file = here("data", "nfl_ftnCharting.RData"))
load(file = here("data", "nfl_playerIDs.RData"))
load(file = here("data", "nfl_rankings.RData"))
load(file = here("data", "nfl_expectedFantasyPoints_weekly.RData"))
load(file = here("data", "nfl_expectedFantasyPoints_offense.RData"))

# Calculated Data
load(file = here("data", "nfl_actualStats_career.RData"))
load(file = here("data", "nfl_actualStats_seasonal.RData"))
```

@@

save(
  nfl_players,
  file = here("data", "nfl_players.RData")
)
```

@@

library("here")

load(file = here("data", "nfl_players.RData"))
```

@@

save(
  nfl_teams,
  file = here("data", "nfl_teams.RData")
)
```

@@

load(file = here("data", "nfl_teams.RData"))
```

@@

save(
  nfl_rosters,
  file = here("data", "nfl_rosters.RData")
)

save(
  nfl_rosters_weekly,
  file = here("data", "nfl_rosters_weekly.RData")
)
```

@@

load(file = here("data", "nfl_rosters.RData"))
load(file = here("data", "nfl_rosters_weekly.RData"))
```

@@

save(
  nfl_schedules,
  file = here("data", "nfl_schedules.RData")
)
```

@@

load(file = here("data", "nfl_schedules.RData"))
```

@@

save(
  nfl_combine,
  file = here("data", "nfl_combine.RData")
)
```

@@

load(file = here("data", "nfl_combine.RData"))
```

@@

save(
  nfl_draftPicks,
  file = here("data", "nfl_draftPicks.RData")
)
```

@@

load(file = here("data", "nfl_draftPicks.RData"))
```

@@

save(
  nfl_depthCharts,
  file = here("data", "nfl_depthCharts.RData")
)
```

@@

load(file = here("data", "nfl_depthCharts.RData"))
```

@@

@@

save(
  nfl_pbp,
  file = here("data", "nfl_pbp.RData")
)
```

@@

@@

@@

save(
  nfl_4thdown,
  file = here("data", "nfl_4thdown.RData")
)
```

@@

@@

save(
  nfl_participation,
  file = here("data", "nfl_participation.RData")
)
```

@@

save(
  nfl_actualStats_offense_weekly, nfl_actualStats_defense_weekly, nfl_actualStats_kicking_weekly,
  file = here("data", "nfl_actualStats_weekly.RData")
)
```

@@

load(file = here("data", "nfl_actualStats_weekly.RData"))
```

@@

save(
  nfl_injuries,
  file = here("data", "nfl_injuries.RData")
)
```

@@

load(file = here("data", "nfl_injuries.RData"))
```

@@

save(
  nfl_snapCounts,
  file = here("data", "nfl_snapCounts.RData")
)
```

@@

load(file = here("data", "nfl_snapCounts.RData"))
```

@@

save(
  nfl_espnQBR,
  file = here("data", "nfl_espnQBR.RData")
)
```

@@

load(file = here("data", "nfl_espnQBR.RData"))
```

@@

save(
  nfl_nextGenStats_weekly,
  file = here("data", "nfl_nextGenStats_weekly.RData")
)
```

@@

load(file = here("data", "nfl_nextGenStats_weekly.RData"))
```

@@

save(
  nfl_advancedStatsPFR,
  file = here("data", "nfl_advancedStatsPFR.RData")
)
```

@@

load(file = here("data", "nfl_advancedStatsPFR.RData"))
```

@@

save(
  nfl_playerContracts,
  file = here("data", "nfl_playerContracts.RData")
)
```

@@

load(file = here("data", "nfl_playerContracts.RData"))
```

@@

save(
  nfl_ftnCharting,
  file = here("data", "nfl_ftnCharting.RData")
)
```

@@

load(file = here("data", "nfl_ftnCharting.RData"))
```

@@

save(
  nfl_playerIDs,
  file = here("data", "nfl_playerIDs.RData")
)
```

@@

load(file = here("data", "nfl_playerIDs.RData"))
```

@@

save(
  nfl_rankings,
  file = here("data", "nfl_rankings.RData")
)
```

@@

load(file = here("data", "nfl_rankings.RData"))
```

@@

save(
  nfl_expectedFantasyPoints_weekly,
  file = here("data", "nfl_expectedFantasyPoints_weekly.RData")
)

save(
  nfl_expectedFantasyPoints_offense,
  file = here("data", "nfl_expectedFantasyPoints_offense.RData")
)
```

@@

load(file = here("data", "nfl_expectedFantasyPoints_weekly.RData"))
load(file = here("data", "nfl_expectedFantasyPoints_offense.RData"))
```

@@

@@

save(
  nfl_actualStats_offense_career, nfl_actualStats_defense_career, nfl_actualStats_kicking_career,
  file = here("data", "nfl_actualStats_career.RData")
)
```

@@

load(file = here("data", "nfl_actualStats_career.RData"))
```

@@

save(
  nfl_actualStats_offense_seasonal, nfl_actualStats_defense_seasonal, nfl_actualStats_kicking_seasonal,
  file = here("data", "nfl_actualStats_seasonal.RData")
)
```

@@

load(file = here("data", "nfl_actualStats_seasonal.RData"))
```

>>>>

# Downloaded Data
load(file = "./data/nfl_players.RData")
load(file = "./data/nfl_teams.RData")
load(file = "./data/nfl_rosters.RData")
load(file = "./data/nfl_rosters_weekly.RData")
load(file = "./data/nfl_schedules.RData")
load(file = "./data/nfl_combine.RData")
load(file = "./data/nfl_draftPicks.RData")
load(file = "./data/nfl_depthCharts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation.RData", fsep = ""))
load(file = "./data/nfl_actualStats_weekly.RData")
load(file = "./data/nfl_injuries.RData")
load(file = "./data/nfl_snapCounts.RData")
load(file = "./data/nfl_espnQBR.RData")
load(file = "./data/nfl_nextGenStats_weekly.RData")
load(file = "./data/nfl_advancedStatsPFR.RData")
load(file = "./data/nfl_playerContracts.RData")
load(file = "./data/nfl_ftnCharting.RData")
load(file = "./data/nfl_playerIDs.RData")
load(file = "./data/nfl_rankings.RData")
load(file = "./data/nfl_expectedFantasyPoints_weekly.RData")
load(file = "./data/nfl_expectedFantasyPoints_offense.RData")

# Calculated Data
load(file = "./data/nfl_actualStats_career.RData")
load(file = "./data/nfl_actualStats_seasonal.RData")
```

@@

save(
  nfl_players,
  file = "./data/nfl_players.RData"
)
```

@@

load(file = "./data/nfl_players.RData")
```

@@

save(
  nfl_teams,
  file = "./data/nfl_teams.RData"
)
```

@@

load(file = "./data/nfl_teams.RData")
```

@@

save(
  nfl_rosters,
  file = "./data/nfl_rosters.RData"
)

save(
  nfl_rosters_weekly,
  file = "./data/nfl_rosters_weekly.RData"
)
```

@@

load(file = "./data/nfl_rosters.RData")
load(file = "./data/nfl_rosters_weekly.RData")
```

@@

save(
  nfl_schedules,
  file = "./data/nfl_schedules.RData"
)
```

@@

load(file = "./data/nfl_schedules.RData")
```

@@

save(
  nfl_combine,
  file = "./data/nfl_combine.RData"
)
```

@@

load(file = "./data/nfl_combine.RData")
```

@@

save(
  nfl_draftPicks,
  file = "./data/nfl_draftPicks.RData"
)
```

@@

load(file = "./data/nfl_draftPicks.RData")
```

@@

save(
  nfl_depthCharts,
  file = "./data/nfl_depthCharts.RData"
)
```

@@

load(file = "./data/nfl_depthCharts.RData")
```

@@

save(
  nfl_pbp,
  file = "./data/nfl_pbp.RData"
)
```

@@

load(file = "./data/nfl_pbp.RData")
```

@@

::: {#nte-download4thDownData .callout-note title="Downloading 4th down data"}
Note: the following code takes a while to run.
:::

```{r}
#| warning: false
#| message: false

@@

save(
  nfl_4thdown,
  file = "./data/nfl_4thdown.RData"
)
```

@@

load(file = "./data/nfl_4thdown.RData")
```

@@

save(
  nfl_participation,
  file = "./data/nfl_participation.RData"
)
```

@@

load(file = "./data/nfl_participation.RData")
```

@@

save(
  nfl_actualStats_offense_weekly, nfl_actualStats_defense_weekly, nfl_actualStats_kicking_weekly,
  file = "./data/nfl_actualStats_weekly.RData"
)
```

@@

load(file = "./data/nfl_actualStats_weekly.RData")
```

@@

save(
  nfl_injuries,
  file = "./data/nfl_injuries.RData"
)
```

@@

load(file = "./data/nfl_injuries.RData")
```

@@

save(
  nfl_snapCounts,
  file = "./data/nfl_snapCounts.RData"
)
```

@@

load(file = "./data/nfl_snapCounts.RData")
```

@@

save(
  nfl_espnQBR,
  file = "./data/nfl_espnQBR.RData"
)
```

@@

load(file = "./data/nfl_espnQBR.RData")
```

@@

save(
  nfl_nextGenStats_weekly,
  file = "./data/nfl_nextGenStats_weekly.RData"
)
```

@@

load(file = "./data/nfl_nextGenStats_weekly.RData")
```

@@

save(
  nfl_advancedStatsPFR,
  file = "./data/nfl_advancedStatsPFR.RData"
)
```

@@

load(file = "./data/nfl_advancedStatsPFR.RData")
```

@@

save(
  nfl_playerContracts,
  file = "./data/nfl_playerContracts.RData"
)
```

@@

load(file = "./data/nfl_playerContracts.RData")
```

@@

save(
  nfl_ftnCharting,
  file = "./data/nfl_ftnCharting.RData"
)
```

@@

load(file = "./data/nfl_ftnCharting.RData")
```

@@

save(
  nfl_playerIDs,
  file = "./data/nfl_playerIDs.RData"
)
```

@@

load(file = "./data/nfl_playerIDs.RData")
```

@@

save(
  nfl_rankings,
  file = "./data/nfl_rankings.RData"
)
```

@@

load(file = "./data/nfl_rankings.RData")
```

@@

save(
  nfl_expectedFantasyPoints_weekly,
  file = "./data/nfl_expectedFantasyPoints_weekly.RData"
)

save(
  nfl_expectedFantasyPoints_offense,
  file = "./data/nfl_expectedFantasyPoints_offense.RData"
)
```

@@

load(file = "./data/nfl_expectedFantasyPoints_weekly.RData")
load(file = "./data/nfl_expectedFantasyPoints_offense.RData")
```

@@

Number of rows:

```{r}
nrow(nfl_players)
```

Number of columns:

```{r}
ncol(nfl_players)
```

@@

save(
  nfl_actualStats_offense_career, nfl_actualStats_defense_career, nfl_actualStats_kicking_career,
  file = "./data/nfl_actualStats_career.RData"
)
```

@@

load(file = "./data/nfl_actualStats_career.RData")
```

@@

save(
  nfl_actualStats_offense_seasonal, nfl_actualStats_defense_seasonal, nfl_actualStats_kicking_seasonal,
  file = "./data/nfl_actualStats_seasonal.RData"
)
```

@@

load(file = "./data/nfl_actualStats_seasonal.RData")
```
